\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=0.82in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{tabularx}
\usepackage{titlesec}

\definecolor{linkblue}{RGB}{0,63,135}
\hypersetup{
  colorlinks=true,
  urlcolor=linkblue,
  linkcolor=linkblue
}
\urlstyle{same}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlist[itemize]{leftmargin=1.2em, topsep=0.2em, itemsep=0.15em, parsep=0em}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{0.12em}\titlerule]
\titlespacing*{\section}{0pt}{1.05em}{0.55em}

\newcommand{\cvheading}[4]{%
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    \textbf{#1} & #2 \\
    \emph{#3} & \emph{#4}
  \end{tabular*}
  \vspace{-0.35em}
}

\newcommand{\simpleentry}[2]{%
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    #1 & #2
  \end{tabular*}
}

\begin{document}

\begin{center}
  {\LARGE \textbf{Archisman Dutta}}\\[0.35em]
  \href{mailto:archisman@cs.au.dk}{archisman@cs.au.dk} \;|\;
  \href{https://archisman.org}{archisman.org} \;|\;
  \href{https://github.com/DeviousCilantro}{github.com/DeviousCilantro}
\end{center}

\section*{Research interests}
Theoretical cryptography; pseudorandom correlations; indistinguishability obfuscation; complexity-theoretic techniques.

\section*{Education}
\cvheading{Aarhus University}{Aarhus, Denmark}{Ph.D. in Computer Science}{Sep 2025 -- present}
\begin{itemize}
  \item Advisors: Peter Scholl and Diego F. Aranha.
  \item Selected coursework: Cryptographic Computing; Succinct Proofs; Cryptologic Protocol Theory; Randomized Algorithms.
\end{itemize}

\cvheading{Ashoka University}{Sonipat, India}{B.Sc. (Hons.) in Mathematics and Computer Science}{Sep 2021 -- May 2024}
\begin{itemize}
  \item CGPA: 3.42/4.00.
  \item Selected coursework: Algorithms; Theory of Computation; Symbolic Logic; Algebra; Probability and Statistics; Computer Security; Elliptic-Curve and Lattice-Based Cryptography.
\end{itemize}

\cvheading{University of Zurich}{Zurich, Switzerland}{Deep Dive into Blockchain summer school}{Jul 2023 -- Aug 2023}
\begin{itemize}
  \item Attended the UZH Blockchain Center summer school on a full scholarship; completed a group project on privacy-preserving CBDC auditing using Pedersen commitments and IPFS.
\end{itemize}

\section*{Manuscripts}
\begin{itemize}
  \item \textbf{ATAVISM: Private Originator Tracing in End-to-End Encrypted Messaging}, with Debayan Gupta and Arup Mondal. Manuscript, 2025.
\end{itemize}

\section*{Research experience}
\cvheading{Aarhus University}{Aarhus, Denmark}{Graduate Research Assistant}{Sep 2025 -- present}
\begin{itemize}
  \item Working on pseudorandom correlation functions for VOLE from DCR-style assumptions, with possible applications to designated-verifier exponent-VRFs and threshold Schnorr signatures.
\end{itemize}

\cvheading{IIT Bombay Trust Lab}{Mumbai, India}{Pre-Doctoral Researcher}{Aug 2024 -- May 2025}
\begin{itemize}
  \item Studied circular-secure publicly verifiable time-lock puzzles and timed commitments from algebraic assumptions.
  \item Reviewed homomorphic and function secret sharing for branching and RMS programs, group correlations, and pseudorandom correlation generators.
  \item Participated in a reading group on proof systems, arguments, and zero knowledge.
\end{itemize}

\cvheading{IIT Bombay Trust Lab}{Mumbai, India}{Summer Research Intern}{May 2024 -- Jul 2024}
\begin{itemize}
  \item Investigated the complexity-theoretic hardness of TFNP subclasses including PPAD, PWPP, PPA, and PLS, with attention to cryptographically relevant Karp reductions.
  \item Studied lattice-based verifiable delay functions, time-lock puzzles, and proofs of sequential work.
\end{itemize}

\cvheading{Ashoka University}{Sonipat, India}{Undergraduate Research Assistant}{Jun 2023 -- Jan 2024}
\begin{itemize}
  \item Contributed to a WhatsApp-funded project on secure originator tracing for end-to-end encrypted messaging, focusing on deployability without revealing intermediate forwarding parties.
  \item Coauthored a manuscript formalizing and benchmarking the protocol against existing alternatives.
  \item Implemented prototype optimizations for number-theoretic transforms and fast modular arithmetic for lattice-based cryptographic operations.
\end{itemize}

\cvheading{Questbook}{Remote / Palo Alto, CA}{Security Research Intern}{Aug 2023 -- Mar 2024}
\begin{itemize}
  \item Improved and benchmarked Groth16 proof generation for Circom R1CS-based circuits in the Reclaim Protocol.
  \item Compiled \texttt{rapidsnark} to platform-agnostic WebAssembly and evaluated proof-system libraries for browser and Node environments.
  \item Studied optimizations for AES and ChaCha20 circuits using arkworks and PLONKish arithmetization.
\end{itemize}

\section*{Teaching}
\cvheading{Aarhus University}{Aarhus, Denmark}{Graduate Teaching Assistant, Distributed Systems and Security}{Jan 2026 -- present}
\begin{itemize}
  \item Grade assignments, hold discussion sessions, and answer student questions in office hours.
\end{itemize}

\begin{itemize}
  \item Lab assistant, public-key cryptography, ACM India winter school on cryptography, IIT Madras, Dec 2024.
  \item Lab lead, fully homomorphic encryption with OpenFHE, ACM India summer school on theoretical foundations of cryptography, IIT Bombay, Jun 2024.
\end{itemize}

\section*{Talks}
\begin{itemize}
  \item Private Originator Tracing in End-to-End Encrypted Messaging. Aarhus Crypto Seminar, Jun 2025.
  \item Time-Lock Puzzles and Verifiable Delay Functions. Student seminar, Oct 2024.
  \item Fully Homomorphic Encryption Lab. ACM India summer school on theoretical foundations of cryptography, Jun 2024.
\end{itemize}

\section*{Service}
\begin{itemize}
  \item External reviewer / subreviewer: EUROCRYPT 2026; CRYPTO 2026.
\end{itemize}

\section*{Fellowships and travel support}
\begin{itemize}
  \item Research Excellence Program for Asia fellowship, Tel Aviv University, 2024 (declined).
  \item Industry scholarship, University of Zurich Blockchain Center summer school, 2023.
  \item Travel support: TCC 2025 (Aarhus University); RWC 2025 (IACR); TPMPC 2025 (IISc); ASIACRYPT 2024 (IIT Bombay Trust Lab).
\end{itemize}

\section*{Technical background}
Rust, Python, C/C++, Go, Linux, shell scripting, Docker, WebAssembly, Circom, LaTeX.

\vfill
{\footnotesize Last updated: May 2026.}

\end{document}
